---
title: Looking to rent a HDB flat in Singapore? 🏠
execute: 
  echo: false
format: html
editor: visual
---

We will investigate the average rental prices of HDB flats and its trends. The scope of this analysis involves rental prices between 2021 to 2023, covering 1 to 5 room flats. The data set used is publicly available [here](https://beta.data.gov.sg/collections/166/view)! 😆

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(sf)
library(mapview)
library(rvest)
library(httr)
library(dplyr)
library(leaflet)
library(plotly)
library(highcharter)
```

```{r message=FALSE, warning=FALSE, echo=FALSE, results='hide'}

test <- read_sf(here::here("MP14_PLNG_AREA_NO_SEA_PL.kml"))

keke <- read_csv("RentingOutofFlats.csv", col_types = cols(
  rent_approval_date = col_character(),
  town = col_character(),
  block = col_character(),
  street_name = col_character(),
  flat_type = col_character(),
  monthly_rent = col_double()
))

rental <- keke %>%
  group_by(town) %>%
  summarize(mean_monthly_rent = mean(monthly_rent))

rental1 <- rental %>%
  rename(Name = town)

meep <- st_read(dsn = "MP14_PLNG_AREA_NO_SEA_PL.kml")

meep_sf <- st_as_sf(meep[c("Name", "geometry")])
meep_sf <- st_set_crs(meep_sf, 3414)

meep_sub <- meep_sf %>%
  select(geometry)

merged_data <- merge(meep_sf, rental1, by.x = "Name", by.y = "Name")

```

### **A heat map of mean rental prices in each planning area**📍

Hover over the area to view the planning area, and click upon it to view the mean rental price! (Edit: WIP in calculating mean per HDB type)

```{r message=FALSE, warning=FALSE, echo=FALSE}

merged_data <- meep_sf %>%
  left_join(rental1, by = c("Name" = "Name"))

popup_content <- sprintf(
  "Town: %s<br>Mean Monthly Rent: $%.2f",
  merged_data$Name,
  merged_data$mean_monthly_rent
)

heatmap_map <- mapview(merged_data, zcol = "mean_monthly_rent", label="Name", popup = popup_content, layer.name = 'Mean Rental Price (SGD)')


heatmap_map

```

<br> Data set for the polygon's coordinates can be found [here](https://beta.data.gov.sg/collections/2104/view)!

#### **Distribution of different HDB types across planning areas** 📊

```{r message=FALSE, warning=FALSE, echo=FALSE}
kekesubset <- keke %>%
  select(town,flat_type) %>%
  group_by(town, flat_type) %>%
  summarise(count=n())

region_mapping <- c(
  "ANG MO KIO" = "North-East",
  "BEDOK" = "East",
  "BISHAN" = "Central",
  "BUKIT BATOK" = "West",
  "BUKIT MERAH" = "West",
  "BUKIT PANJANG" = "West",
  "BUKIT TIMAH" = "Central",
  "CENTRAL" = "Central",
  "CHOA CHU KANG" = "West",
  "CLEMENTI" = "West",
  "GEYLANG" = "Central",
  "HOUGANG" = "North-East",
  "JURONG EAST" = "West",
  "JURONG WEST" = "West",
  "KALLANG/WHAMPOA" = "Central",
  "MARINE PARADE" = "Central",
  "PASIR RIS" = "East",
  "PUNGGOL" = "North-East",
  "QUEENSTOWN" = "Central",
  "SEMBAWANG" = "North",
  "SENGKANG" = "North-East",
  "SERANGOON" = "North-East",
  "TAMPINES" = "East",
  "TOA PAYOH" = "Central",
  "WOODLANDS" = "North",
  "YISHUN" = "North")

kekesubset$region <- region_mapping[kekesubset$town]

#Segregating bar graphs into different regions
north <- kekesubset %>%
  filter(region=="North") %>%
  group_by(town, flat_type) %>%
  summarize(total_count = sum(count))

northeast <- kekesubset %>%
  filter(region=="North-East") %>%
  group_by(town, flat_type) %>%
  summarize(total_count = sum(count))

east <- kekesubset %>%
  filter(region=="East") %>%
  group_by(town, flat_type) %>%
  summarize(total_count = sum(count))

west <- kekesubset %>%
  filter(region=="West") %>%
  group_by(town, flat_type) %>%
  summarize(total_count = sum(count))

central <- kekesubset %>%
  filter(region=="Central") %>%
  group_by(town, flat_type) %>%
  summarize(total_count = sum(count))

totalcount <- kekesubset %>%
  group_by(flat_type) %>%
  summarize(total_count=sum(count))

#Adding year column
keke <- keke %>%
  mutate(year = substr(rent_approval_date, 1, 4)) 

trend <- keke %>%
  group_by(town,year) %>%
  summarize(mean_monthly_rent = mean(monthly_rent))

trend$mean_monthly_rent <- round(trend$mean_monthly_rent, 2)

```

```{r message=FALSE, warning=FALSE, echo=FALSE}
hchart(totalcount, "bar", hcaes(x = flat_type, y = total_count)) %>%
  hc_title(text = "Overall Total Count of Flat Types") %>%
  hc_xAxis(title = list(text = "Flat Type")) %>%
  hc_yAxis(title = list(text = "Total Count")) %>%
  hc_legend(align = "right", layout = "vertical") %>%
  hc_chart(type = "bar", backgroundColor = "#ededff")

```

Generally, 4-room flats are the most abundant type of HDB rental. Below, we will be able to see the distribution of HDB rentals across regions and individual planning areas.

###### **Central**

```{r message=FALSE, warning=FALSE, echo=FALSE}

hchart(central, "bar", hcaes(x = town, y = total_count, group = flat_type)) %>%
  hc_title(text = "Total Count of Flat Types in the Northeast Region") %>%
  hc_xAxis(title = list(text = "Planning Area")) %>%
  hc_yAxis(title = list(text = "Total Count")) %>%
  hc_legend(align = "right", layout = "vertical") %>%
  hc_chart(type = "bar", backgroundColor = "#ededff") %>%
  hc_caption(
    text = "Hover over the line graphs to get the specific planning area's data",
    useHTML = TRUE)

```

<br>

###### **East**

```{r message=FALSE, warning=FALSE, echo=FALSE}

hchart(east, "bar", hcaes(x = town, y = total_count, group = flat_type)) %>%
  hc_title(text = "Total Count of Flat Types in the East Region") %>%
  hc_xAxis(title = list(text = "Planning Area")) %>%
  hc_yAxis(title = list(text = "Total Count")) %>%
  hc_legend(align = "right", layout = "vertical") %>%
  hc_chart(type = "bar", backgroundColor = "#ededff") %>%
  hc_caption(
    text = "Hover over the line graphs to get the specific planning area's data",
    useHTML = TRUE)

```

<br>

###### **North**

```{r message=FALSE, warning=FALSE, echo=FALSE}

hchart(north, "bar", hcaes(x = town, y = total_count, group = flat_type)) %>%
  hc_title(text = "Total Count of Flat Types in the North Region") %>%
  hc_xAxis(title = list(text = "Planning Area")) %>%
  hc_yAxis(title = list(text = "Total Count")) %>%
  hc_legend(align = "right", layout = "vertical") %>%
  hc_chart(type = "bar", backgroundColor = "#ededff") %>%
  hc_caption(
    text = "Hover over the line graphs to get the specific planning area's data",
    useHTML = TRUE)

```

<br>

###### **North-East**

```{r message=FALSE, warning=FALSE, echo=FALSE}

hchart(northeast, "bar", hcaes(x = town, y = total_count, group = flat_type)) %>%
  hc_title(text = "Total Count of Flat Types in the Northeast Region") %>%
  hc_xAxis(title = list(text = "Planning Area")) %>%
  hc_yAxis(title = list(text = "Total Count")) %>%
  hc_legend(align = "right", layout = "vertical") %>%
  hc_chart(type = "bar", backgroundColor = "#ededff") %>%
  hc_caption(
    text = "Hover over the line graphs to get the specific planning area's data",
    useHTML = TRUE)

```

<br>

###### **West**

```{r message=FALSE, warning=FALSE, echo=FALSE}

hchart(west, "bar", hcaes(x = town, y = total_count, group = flat_type)) %>%
  hc_title(text = "Total Count of Flat Types in the West Region") %>%
  hc_xAxis(title = list(text = "Planning Area")) %>%
  hc_yAxis(title = list(text = "Total Count")) %>%
  hc_legend(align = "right", layout = "vertical") %>%
  hc_chart(type = "bar", backgroundColor = "#ededff") %>%
  hc_caption(
    text = "Hover over the line graphs to get the specific planning area's data",
    useHTML = TRUE)

```

<br>

#### **Trend in rental prices over the 3 years** 📈

```{r message=FALSE, warning=FALSE, echo=FALSE}
line_chart <- hchart(trend, "line", hcaes(x = year, y = as.numeric(mean_monthly_rent), group = town)) %>%
  hc_title(text = "Mean Monthly Rent Over Years") %>%
  hc_xAxis(title = list(text = "Year")) %>%
  hc_yAxis(title = list(text = "Mean Monthly Rent")) %>%
  hc_legend(align = "right", layout = "vertical") %>%
  hc_chart(type = "line", backgroundColor = "#ededff") %>%
  hc_caption(
    text = "Hover over the line graphs to get the specific planning area's data",
    useHTML = TRUE)

line_chart
```

<br>

Despite the limitation of the data set having only 3 years of data, it is evident that there is a consistent increasing trend across all planning areas. Further, it is observed that the increase in rental prices are relatively unanimous as well.

### Placeholder title for further analysis 🫧

Placeholder text

```         
```
